---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---
```{r pkg-knitr-opts, include=FALSE}
hrbrpkghelpr::global_opts()
```

```{r badges, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::stinking_badges()
```

```{r description, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::yank_title_and_description()
```

## What's Inside The Tin

The following functions are implemented:

```{r ingredients, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::describe_ingredients()
```

## Installation

```{r install-ex, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::install_block()
```

## Usage

```{r lib-ex}
library(brimr)
library(tibble)

# current version
packageVersion("brimr")

```

### Available Brim "spaces"

```{r available-brim-spaces}
brim_spaces()
```

### Sample ZQL query

```{r sample-zql-query}
# Z query to fetch Zeek connection data to create our network connection graph
zql1 <- '_path=conn | count() by id.orig_h, id.resp_h, id.resp_p | sort id.orig_h, id.resp_h, id.resp_p'

cat(
  substr(jsonlite::toJSON(jsonlite::fromJSON(brim_ast(zql1)), pretty = TRUE), 1, 100), "..."
)
```

### Let's execute the query

```{r zeek-query-execution}
space <- "2021-02-17-Trickbot-gtag-rob13-infection-in-AD-environment.pcap"

r1 <- brim_search(space, zql1)

r1

(r1 <- as_tibble(tidy_brim(r1)))
```

### Let's try one that processes the Suricata alerts

```{r suricata-query-execution}
# Z query to fetch Suricata alerts including the count of alerts per source:destination 
zql2 <- "event_type=alert | count() by src_ip, dest_ip, dest_port, alert.severity, alert.signature | sort src_ip, dest_ip, dest_port, alert.severity, alert.signature"

r2 <- brim_search(space, zql2)

r2

(r2 <- (as_tibble(tidy_brim(r2))))
```

```{r graph, fig.width = 9}
library(igraph)
library(ggraph)
library(tidyverse)

gdf <- count(r1, orig_h, resp_h, wt=count)

count(gdf, node = resp_h, wt=n, name = "in_degree") %>% 
  full_join(
    count(gdf, node = orig_h, name = "out_degree")
  ) %>% 
  mutate_at(
    vars(in_degree, out_degree),
    replace_na, 1
  ) %>% 
  arrange(in_degree) -> vdf

g <- graph_from_data_frame(gdf, vertices = vdf)

ggraph(g, layout = "linear") +
  geom_node_point(
    aes(size = in_degree), shape = 21
  ) +
  geom_edge_arc(
    width = 0.125, 
    arrow = arrow(
      length = unit(5, "pt"),
      type = "closed"
    )
  )
```

## brimr Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a Contributor Code of Conduct. 
By participating in this project you agree to abide by its terms.
